%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[blue]{casualg}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classicg}                % idem
%\moderncvtheme[roman]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{hyperref}

% adjust the page margins
\usepackage[scale=0.84]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Gonzalo}
\familyname{Alvarez}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{C/ Santuario Valverde 6}{28049, Madrid}    % optional, remove the line if not wanted
\mobile{0034 678 252 458}                      % optional, remove the line if not wanted
% \fax{fax (optional)}                          % optional, remove the line if not wanted
\email{gonzaloab@gmail.com}                      % optional, remove the line if not wanted
\website{www.gon.al}
\extrainfo{León (Spain), 12.31.1981} % optional, remove the line if not wanted
%\photo[64pt]{picture.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
% \quote{}                 % optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


\newenvironment{pitems}{
	\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
}{\end{itemize}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2000--2007}{Master's Degree in Telecommunications Engineering}{Vigo University}{}{}{}  % arguments 3 to 6 are optional
\cventry{2005--2007}{Master's Final Project}{Vigo University}{ASP Web Environment development}{}{}{}

\section{Work Experience}
\ccventry{2013--Present}{Senior Software Development Engineer at Amazon.com}{}{Madrid, Spain}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Softlines CX Backend/Frontend Engineer:} Design and development of Java based architectures within the Softlines CX team using
	technologies like Spring, Oracle, Backbone, Handlebars, Tomcat and Memcache, among others.
\item $-$ \textsl{Scrum Master:} Management of a team of software engineers targeting the development of a project using Agile tecnologies and techniques,
	such as Scrum, Kanban or Lean.
\end{pitems}}

\ccventry{2011--2013}{Senior Systems and Software Architect at The Server Labs}{}{Madrid, Spain}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Software Engineer for BBVA:} Development of a Web Platform for the BBVA Bank based on J2EE and Maven using the well known Controller-Service-DAO 
	pattern based on the Spring Framework for the backend with JPA to connect to the OracleDB and JavaServer Faces and Primefaces for the presentation layer. 
	It has been developed following modern CI standards based on Maven and Hudson/Jenkins.
\item $-$ \textsl{SimCloud Architect Engineer:} Design, implementation and testing of a Private Cloud Environment solution for the
	European Space Agency based on VMWare ESXi, OpenNebula and Chef with its own, custom developed, Web Interface.	
\item $-$ \textsl{Cloud Architect:} Design, implementation and operational support of several cloud based solutions for multinational corporations
	and organizations like ESA, Decathlon or ICCAT. Intensive usage of AWS Solutions, such as EC2, S3, VPC, Route53, ELB, AutoScaling or RDS.
\item $-$ \textsl{Continuous Integration Architect:} Deployment and management of CI environments on the Amazon Cloud based on Hudson/Jenkins, SVN and Jira.
\end{pitems}}
\ccventry{2009--2011}{Systems and Software Engineer at European Space Agency Operation Centre (ESOC/ESA)}{OPS-GIB Section}{Darmstadt, Germany}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Scrum Master and Software Engineer:} Developer and Software Architect of several applications used in
	the ESTRACK Ground Stations in line with the European Space Ground Operations Software, such as EUDGSSC or the EUD MIMICS based on Java and Maven.
\end{pitems}}
\ccventry{}{}{}{}{
\begin{pitems}
\item $-$ \textsl{Validation Engineer:} Definition and application of validation procedures and documentation for several 
	projects deployed on ESA Ground Stations like FIDES (File Disseminator for ESTRACK Ground Stations) or 
	FARC (File Archive used as SCOS telemetry storage).
\item $-$ \textsl{TMTCS Engineer:} Technical responsible for the Telemetry and Telecommand System maintenance. In charge of the
	continous validation and integration of the system. Creation of the appropiate SPRs, SCRs and Technical Notes related
	to the day-to-day work by using several tools, such as DOORS, Mercury Quality Center and Synergy Database. Participation in
	the Radio Frequency Compatibility Test (RFCT) on the TMTCS side for several missions, such as Yinghuo or Fobos-Grunt.
    Adaptation of the TMTCS to the ESA Mission Gaia for achieving the highly demanding telemetry rates on the Ground Station
	Infrastructure.
\item $-$ \textsl{Server Administrator:} System administrator of the Ground Infrastructure Back-end Server used for
	active development activities and documentation. Setup of the system using Continuous Integration tools, like SVN,
	Hudson, Trac, Ant, IceScrum among others.
\item $-$ \textsl{Technical Consultor:} Participation in Technical Comitees and Task Forces as Advisor in many internal
	projects and activities, such as FEC Evolution, STC2 and GSMC.
\end{pitems}}
\ccventry{2008--2009}{Young Graduate Trainee at ESOC/ESA}{OPG-GIB Section}{Darmstadt, Germany}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Validation Engineer:} Technical advisor and supervisor of the Factory Acceptance Tests for the
	Egos User Desktop and Technical manager for the Site Acceptance Tests. Validation of FARC from S2K for its use
	with FIDES under the EGOS Model. 
\item $-$ \textsl{Software Engineer:} Technical revision for the requirements of the MIMIC project and development 
	of an internal prototype based on Eclipse using EMF, GEF and GMF.
\item $-$ \textsl{Documentation: } Creation of several Technical Notes, SRSs, ICDs, MoMs and other internal documents.
\end{pitems}}
\cventry{2007--2007}{Teacher of Project Management}{Project management seminars provided to IMERYS IKF Inc.}{A Guarda, Pontevedra, Spain}
{Enterprise course teacher for Norformacion - Fundación Tripartita to IMERYS IKF Inc. about Project Management theorical aspects and the use
of the Microsoft Project for designing Gantt Diagrams and keeping track of the project changes}{}
\cventry{2005--2006}{Contracted Researcher}{Vigo University, Spain}{Development of JPoEML, 
	a Java tool (mimic oriented) for designing and producing an E-Learning web environment that uses XML and J2EE to serve
	the desired learning models to the users over the web. This tool, created from scratch and based on the popular JFreeChart 
	Java Library, presented an editing environment similar to a UML Designing Tool used for creating and editing Learning Environments}{}{}
\cventry{1999--2005}{Network Administrator and Web Developer}{Freelance web developer and network administrator for local 
	and national enterprises. Design and deployment of a set of VPNs to provide media content to final clients through a Web
	Environment}{Vigo, Spain}{}{}

\section{Papers and Conferences}
\cventry{Jun 2013}{SimCloud Paper and Presentation}{ESA Workshop}{ESOC, Darmstadt, Germany}{SimCloud: an Operational Simulator Development and Validation Cloud}{}

\pagebreak

\section{Professional Training}
\cventry{Jun 2014}{Interviewing Software Engineers}{Amazon.com}{Amazon Spain, Madrid}{Theoretical and practical approach to hire the best software engineers by identifying their weakness and strengths}{}
\cventry{May 2013}{AWS Technical Professional}{The Server Labs}{Amazon.com}{AWS training targetting IT professionals designing Cloud architectures based on customer business requirements.}{}
\cventry{Apr 2010}{Agile Development Technologies}{The Server Labs}{ESOC, Darmstadt, Germany}{Software Development using Agile Metodology and SCRUM Techniques}{}
\cventry{Feb 2009}{Eclipse EMF, GEF and GMF Technologies}{OBEO Eclipse Foundation Member}{ESOC, Darmstadt, Germany}{Development of Eclipse Applications based on EMF/GEF and GMF}{}{}

\section{Languages}
\cvlanguage{Spanish}{Mother Tongue}{}
\cvlanguage{English}{Fluent}{More than eight years as primary professional language.}
\cvlanguage{German}{Good}{More than three years living in Germany, Goethe Institut level B2.}
\cvlanguage{Italian}{Basic}{Internal courses at ESOC/ESA.}

\section{Software Development}
%\cvskill{Linear}{Assembler, C, Pascal, Cobol, Fortran, Lisp.}
%\cvskill{Object Oriented}{Java, C++, Delphi, Visual Basic.}
\cvskill{Languages}{Java, C/C++, Pascal, Fortran, Delphi, Visual Basic.}
\cvskill{Eclipse}{PDE, RCP, SWT, EMF, GEF, GMF, OCL.}
\cvskill{J2EE}{JSF, JPA, Hibernate, JAX-RS, JAX-WS, Liquibase, Spring, Jersey.}
%\cvskill{Distributed}{RCP, Java RMI, CORBA.}
\cvskill{Scripting}{Python, Bash, Tcl, Perl.}
\cvskill{Web}{PHP, ASP, JSP, GWT, DHTML, XML, CSS, JS, Grunt, Handlebars}
\cvskill{CI}{Hudson/Jenkins, Maven, Jira, SVN, Redmine, Trac, Ant.}
%\cvskill{Agile}{Agilefant, IceScrum, XPlanner}
\cvskill{Others}{SQL, TestLink, \TeX.}

\section{Computer Environments}
\cvline{Unix}{Debian/SUSE/RedHat Linux, Solaris and Irix System Administration. LAMP.}
\cvline{Networking}{HTTP, DNS, SMTP, FTP, LDAP, Samba, DHCP, SSH, NFS, Security.}
\cvline{Virtualization}{Xen/XCP/XenServer, OpenVZ, VirtualBox, ESXi, Docker.}
\cvline{Public Cloud}{Amazon Web Services, CloudSigma, Google Compute Engine, CloudBees, Heroku.}
\cvline{Private Cloud}{OpenStack, OpenNebula, Eucalyptus.}
\cvline{Provisioning}{Chef, Puppet, Fabric.}
\cvline{J2EE Platforms}{Apache Tomcat, IBM Websphere, JBoss AS.}
\cvline{Space}{CCSDS TM/TC/SLE/CFDP, ECSS SW Standards}

\section{Documentation and References}
\cvline{}{\slshape{Available upon Request.}}
\end{document}


%% end of file `template_en.tex'.
