% LaTeX file for resume 
% This file uses the resume document style (res.sty)
% \documentstyle[margin]{res} 
\documentclass[margin]{res} 
% Use \documentstyle[margin,helvetica]{res} for helvetica postscript font
% Use \documentstyle[margin]{res} to get default (Computer Modern) font 
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10.5in} % increase text height to fit resume on 1 page
\usepackage[spanish]{babel}
\renewcommand{\shorthandsspanish}{}
\usepackage{eurosym}

\begin{document} 
{\vspace*{1cm}}
\name{\vspace{3mm}GONZALO F. ALVAREZ BARRIO}
\address{ galvarez@det.uvigo.es \\ Torrecedeira 67 6ºF \\   Vigo, Pontevedra 36202 \\   0034 678 252 458 }
                           
                        
\begin{resume}                        
 
\section{EDUCATION}       Master Degree in Telecommunications Engineering at Vigo University. Spain.
 
\section{SKILLS} 
\normalsize{\section{Programming Languages}}
                 \begin{itemize}
                 \item \textit{Linear:} C Assembler Pascal Cobol Fortran Lisp
				 \item \textit{Objects Oriented:} Java C++ Delphi Visual Basic
				 \item \textit{Distributed:} RPC Java RMI CORBA
				 \item \textit{Web:} PHP ASP JSP Servlets HTML DHTML XML CSS JavaScript AJAX 
				 \item \textit{DataBases:} SQL
				 \item \textit{Text Processor:} \TeX
                 \end{itemize}
\normalsize{\section{Environments}} 
                 \begin{itemize}
                  \item LAMP Expert (Linux Apache MySql PHP)
				  \item Debian RedHat and SuSe Linux Networks and System Administration
				  \item HP-UX Solaris Irix 
				  \item Microsoft Windows NT/XP/2003  Network (IIS \& SQLServer) and System Administration and W32 API advanced programming skills
				  \item DHCP SMTP Samba HTTP FTP Tomcat (Jakarta) DNS SSH NFS WebMin
                  \end{itemize}
\normalsize{\section{Software Engineering}} 
                 \begin{itemize}
				  \item Project Management (MS Project \& OpenProj)
				  \item Architectural Patterns expert
				 \end{itemize}

\section{LANGUAGES}
		\begin{itemize}
			\item \textit{Spanish:} Mother Tongue.
			\item \textit{English:} Fluent - Summer 1997 and 1998 living in Markham - Downtown Toronto - Canada.
			\item \textit{German:} Basic level courses at Centro de Linguas - Vigo University.
		\end{itemize}

\section{EXPERIENCE}      
         \begin{tabular}{p{3in} r} % setup 2 columns, first
					    % is 3 inches wide
                  Freelance Web Developer &   2000 - 2005
           \end{tabular}	
                   \begin{itemize} % \item[] prevents a bullet from appearing
                    \item[] Creation of Websites for local enterprises
		   \end{itemize} 
		 \begin{tabular}{p{3in} r}
                  Network Resources Admin &  2005
                 \end{tabular}	
		  \begin{itemize}
                   \item[] www.cmprisk.com, www.hotelutopia.es, www.netia.es \ldots
          \end{itemize}
		  \begin{tabular}{p{3in} r}
		  		Final Project &  2006
			\end{tabular}
			\begin{itemize}
				\item[] Adaptation of an ASP Web Environment to European, Spanish and local laws concerning on security and data privacy and the creation of documents for the customer about security directives and rules.
			\end{itemize}
		\begin{tabular}{p{3in} r}
				Employed as a Researcher for Vigo University &  Feb - Nov 2006
			\end{tabular}
			\begin{itemize}
				\item[] Project Leader in the development of a Java application and a Server Enviroment for PoEML named JPoeml. More info at www.poeml.com
			\end{itemize}
		\begin{tabular}{p{3in} r}
				Teacher of Project Management & Oct - Nov 2007
			\end{tabular}
			\begin{itemize}
				\item[] Project Management seminars for IMERYS IKF Inc. with Norformacion - Fundacion Tripartita using Microsoft Project 2007.
\section{REFERENCES}\hspace{2mm}Available on Request.
\end{resume} 
\end{document}
