%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[blue]{casualg}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{classicg}                % idem
%\moderncvtheme[roman]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{hyperref}

% adjust the page margins
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Gonzalo}
\familyname{Alvarez}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{Frankfurter Strasse 11}{64293 - Darmstadt (Germany)}    % optional, remove the line if not wanted
\mobile{0049 176 7715 1929}                    % optional, remove the line if not wanted
\altmobile{0034 678 252 458}                      % optional, remove the line if not wanted
% \fax{fax (optional)}                          % optional, remove the line if not wanted
\email{gonzaloab@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{León (Spain), 12.31.81} % optional, remove the line if not wanted
%\photo[64pt]{picture.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
% \quote{}                 % optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


\newenvironment{pitems}{
	\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
}{\end{itemize}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2000--2007}{Master's Degree in Telecommunications Engineering}{Vigo University}{}{}{}  % arguments 3 to 6 are optional
\cventry{2005--2007}{Master's Final Project}{Vigo University}{ASP Web Environment development}{}{}{}

\section{Work Experience}
\ccventry{2009--Today}{System and Software Engineer at European Space Agency Operation Centre (ESOC/ESA)}{Serco Contractor on site at ESOC/ESA OPS-GIB Section}{Darmstadt, Germany}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Validation Engineer:} Definition and application of validation procedures and documentations for several 
	projects deployed on ESA Ground Stations like FIDES (File Disseminator for ESTRACK Ground Stations) or 
	FARC (File Archive used as SCOS telemetry storage).
\item $-$ \textsl{TMTCS Engineer:} Technical responsible for the Telemetry and Telecommand System maintenance. In charge of the
	continous validation and integration of the system. Creation of the appropiate SPRs, SCRs and Technical Notes related
	to the day-to-day work by using several tools, such as DOORS, Mercury Quality Center and Synergy.
\item $-$ \textsl{Scrum Master and Software Engineer:} Developer and Software Architect of several applications used in
	the ESTRACK Ground Stations in line with the European Space Ground Operations Software, such as EUDGSSC (a Rich Client
	Application for interacting with the Subsystems Controllers) or the EUD MIMICS (a mimic platform to provide a graphical
	environment for the EGOS Applications).
\item $-$ \textsl{Server Administrator:} System administrator of the Ground Infrastructure Back-end Server used for
	active development activities and documentation.
\item $-$ \textsl{Technical Consultor:} Participation in Technical Comitees and Task Forces as Advisor in many internal
	projects and activities, such as FEC Evolution, STC2, GSMC and so on.
\end{pitems}}
\ccventry{2008--2009}{YGT at ESOC/ESA}{Young Graduate Trainee at ESOC/ESA OPG-GIB Section}{Darmstadt, Germany}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Validation Engineer:} Technical advisor and supervisor of the Factory Acceptance Tests for the
	Egos User Desktop and Technical manager for the Site Acceptance Tests.
\item $-$ \textsl{Software Engineer:} Technical revision for the requirements of the MIMIC project and development 
	of an internal prototype based on Eclipse using EMF, GEF and GMF. 
\end{pitems}}
\cventry{2007--2007}{Teacher of Project Management}{Project management seminars provided to IMERYS IKF Inc.}{A Guarda, Pontevedra, Spain}{Enterprise course teacher for Norformacion - Fundación Tripartita to IMERYS IKF Inc}{}
\cventry{2005--2006}{Contracted Researcher}{Vigo University, Spain}{Development of JPoEML, 
	a Java tool (mimic oriented) for designing and producing an E-Learning web environment that uses XML and J2EE to serve
	the desired learning models to the users over the web}{}{}
\cventry{1999--2005}{Network Administrator and Web Developer}{Freelance web developer and network administrator for local 
	and national enterprises}{Vigo, Spain}{}{}

\section{Professional Training}
\cventry{Apr 2010}{Agile Development Technologies}{The Server Labs}{ESOC, Darmstadt, Germany}{Software Development using Agile Metodology and SCRUM Techniques}{}
\cventry{Feb 2009}{Eclipse EMF, GEF and GMF Technologies}{OBEO Eclipse Foundation Member}{ESOC, Darmstadt, Germany}{Development of Eclipse Applications based on EMF/GEF and GMF}{}{}


\section{Languages}
\cvlanguage{Spanish}{Mother Tongue}{}
\cvlanguage{English}{Fluent}{Three years working in English at the European Space Agency. Six months living in Toronto, Canada.}
\cvlanguage{German}{Good}{Three years living in Germany, Goethe Institut level B2.}
\cvlanguage{Italian}{Basic}{Internal courses at ESOC/ESA.}

\section{Software Development}
\cvskill{Linear}{Assembler, C, Pascal, Cobol, Fortran, Lisp.}
\cvskill{Object Oriented}{C++, Java, Delphi, Visual Basic.}
\cvskill{Eclipse}{PDE, RCP, SWT, EMF, GEF, GMF, OCL.}
\cvskill{Distributed}{RCP, Java RMI, CORBA.}
\cvskill{Scripting}{Python, Bash, Tcl, Perl.}
\cvskill{Web}{PHP, ASP, JSP, DHTML, XML, CSS, JS, AJAX.}
\cvskill{Others}{SQL, \TeX.}

\section{Computer Environments}
\cvline{Unix}{Debian and RedHat Linux, Solaris and Irix System Administration. LAMP.}
\cvline{Windows}{NT/XP/2003/7 System Administration.}
\cvline{Networking}{HTTP, DNS, SMTP, FTP, Samba, DHCP, SSH, NFS, Security.}

\section{Documentation and References}
\cvline{}{\slshape{Available upon Request.}}

\end{document}


%% end of file `template_en.tex'.
