%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[blue]{casualg}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[roman]{casualg}                % idem
%\moderncvtheme[roman]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{hyperref}
\usepackage{fmtcount}
\usepackage{fontawesome}

% adjust the page margins
\usepackage[scale=0.84]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Gonzalo}
\familyname{Alvarez}
% \title{Curriculum Vitae}               % optional, remove the line if not wanted
%\address{Seattle, WA}{Green Card Holder}    % optional, remove the line if not wanted
\mobile{206 883 7479}                      % optional, remove the line if not wanted
% \fax{fax (optional)}                          % optional, remove the line if not wanted
\email{gonzaloab@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{\faMapMarker \, Seattle, WA \, {\color{sectiontitlecolor}$\bullet$ } \, \faCheck \, Green Card Holder}
% \website{www.gon.al}
%\extrainfo{León (Spain), 12.31.1981} % optional, remove the line if not wanted
%\photo[64pt]{picture.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
% \quote{}                 % optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


\newenvironment{pitems}{
	\begin{itemize}
	\setlength{\itemsep}{0.8pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
}{\end{itemize}}

\newcommand*{\bulletitem}{{\color{sectiontitlecolor}$\bullet$ }}
%\item \bulletitem \textsl{Long Term Architecture:} Defined and delivered the high level architecture for Alexa Enterprise products supporting 5+ large businesses, 40+ services owned by more than 30 teams.

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Experience}
\ccventry{2017--Present}{Principal Software Engineer}{Amazon Alexa}{Seattle, WA}
{. 
\begin{pitems}
\item \bulletitem \textsl{Long Term Achitecture \& Business Alignement:} Defined the high level architecture for B2B products in Alexa, which enabled 500+ businesses to use Alexa for their customers in several segments, including
    hospitality, residential, workplace, healthcare and senior living. Influenced planning strategy, and objectives for Alexa to increase bottom-line impact for B2B Amazon customers.
\item \bulletitem \textsl{Product Delivery Focus:} Delivered 150+ Public APIs, UI interfaces and SDKs for an ecosystem of 3P developers to integrate Alexa in their offerings,
    which allowed 60+ 3P companies to offer voice technologies as part of their products, with low integration effort and high business value.
\item \bulletitem \textsl{Senior Engineering Leadership:} Mentored and grew 20+ engineers to different leves, and created a technical excellence culture in the team building mechanisms that allowed junior engineers
    to get help and grow, and senior engineers to lead innitiatives and achieve their aspirations.
\item \bulletitem \textsl{Cross Organizational Partnerships:} Worked across organizational boundaries to align programs and deliverables across business and technical leaders at Director and VP level, helping Alexa teams realize
    monetization opportunities in the enterprise segment, whilst delivering high engagement capabilities for consumers.
\item \bulletitem \textsl{Critical Path Software Development:} Implemented 30+ critical and foundational software pieces in highly ambiguous environments that enabled teams to align on direction and businesses to unblock.
\end{pitems}}

\ccventry{2013--2017}{Senior Software Engineer}{Amazon.com}{Seattle, WA}
{. 
\begin{pitems}
\item \bulletitem \textsl{Technical Leader Retail Checkout:} Led design and critical path implementations for all Amazon Retail Checkout Experiences, including Buy Now, One Click and Mobile, and defined the path to transition
    the tech stack from Perl-based monolith to Java-based SOA.
\item \bulletitem \textsl{Retail API Delivery:} Implemented and delivered Checkout Rest APIs enabling more than 10+ consumer products to create transactional purchase experiences for customers, lowering checkout experience
    development from 2 dev/years to less than 3 dev/months.
\item \bulletitem \textsl{Softlines CX Backend/Frontend Engineer:} Design and development of Java based architectures within the Softlines CX team using
	technologies like Spring, Oracle, Backbone, Handlebars, Tomcat and Memcache.
\item \bulletitem \textsl{Scrum Master \& Team Lead:} Mentor and led a team of software engineers and defined processes, such as Agile/Scrum, to increase product delivery pace and predictibility.
\end{pitems}}

\ccventry{2011--2013}{Senior Systems and Software Architect}{The Server Labs Ltd}{Madrid, Spain}
{.
\begin{pitems}
\item \bulletitem \textsl{ESA Contractor - Software Architect:} Design, implementation and testing of a Private Cloud Environment solution for the
	European Space Agency based on VMWare ESXi, OpenNebula and Chef with its own, custom developed, Web Interface.	
\item \bulletitem \textsl{Finref Contractor - Engineer Lead:} Development of a Web Platform for the BBVA Bank based on J2EE and Maven using the well known Controller-Service-DAO 
	pattern based on the Spring Framework for the backend with JPA to connect to the OracleDB and JavaServer Faces and Primefaces for the presentation layer. 
\item \bulletitem \textsl{Cloud Lead Architect:} Design, implementation and operational support of several cloud based solutions for multinational corporations
	and organizations like ESA, Decathlon or ICCAT. Intensive usage of AWS Solutions, such as EC2, S3, VPC, Route53, ELB, AutoScaling or RDS.
\end{pitems}}

\ccventry{2009--2011}{Systems and Software Engineer at European Space Agency Operation Centre (ESOC/ESA)}{OPS-GIB Section}{Darmstadt, Germany}
{.
\begin{pitems}
\item $-$ \textsl{Scrum Master and Software Engineer:} Developer and Software Architect of several applications used in
	the ESTRACK Ground Stations in line with the European Space Ground Operations Software, such as EUDGSSC or the EUD MIMICS based on Java and Maven.
%\end{pitems}}
%\ccventry{}{}{}{}{
%\begin{pitems}
\item $-$ \textsl{Validation Engineer:} Definition and application of validation procedures and documentation for several 
	projects deployed on ESA Ground Stations like FIDES (File Disseminator for ESTRACK Ground Stations) or 
	FARC (File Archive used as SCOS telemetry storage).
\item $-$ \textsl{TMTCS Engineer:} Technical responsible for the Telemetry and Telecommand System maintenance. In charge of the
	continous validation and integration of the system. Creation of the appropiate SPRs, SCRs and Technical Notes related
	to the day-to-day work by using several tools, such as DOORS, Mercury Quality Center and Synergy Database. Participation in
	the Radio Frequency Compatibility Test (RFCT) on the TMTCS side for several missions, such as Yinghuo or Fobos-Grunt.
    Adaptation of the TMTCS to the ESA Mission Gaia for achieving the highly demanding telemetry rates on the Ground Station
	Infrastructure.
\item $-$ \textsl{Server Administrator:} System administrator of the Ground Infrastructure Back-end Server used for
	active development activities and documentation. Setup of the system using Continuous Integration tools, like SVN,
	Hudson, Trac, Ant, IceScrum among others.
\item $-$ \textsl{Technical Consultor:} Participation in Technical Comitees and Task Forces as Advisor in many internal
	projects and activities, such as FEC Evolution, STC2 and GSMC.
\end{pitems}}
\ccventry{2008--2009}{Young Graduate Trainee at ESOC/ESA}{OPG-GIB Section}{Darmstadt, Germany}
{. Activities:
\begin{pitems}
\item $-$ \textsl{Validation Engineer:} Technical advisor and supervisor of the Factory Acceptance Tests for the
	Egos User Desktop and Technical manager for the Site Acceptance Tests. Validation of FARC from S2K for its use
	with FIDES under the EGOS Model. 
\item $-$ \textsl{Software Engineer:} Technical revision for the requirements of the MIMIC project and development 
	of an internal prototype based on Eclipse using EMF, GEF and GMF.
\item $-$ \textsl{Documentation: } Creation of several Technical Notes, SRSs, ICDs, MoMs and other internal documents.
\end{pitems}}
\cventry{2007--2007}{Teacher of Project Management}{Project management seminars provided to IMERYS IKF Inc.}{A Guarda, Pontevedra, Spain}
{Enterprise course teacher for Norformacion - Fundación Tripartita to IMERYS IKF Inc. about Project Management theorical aspects and the use
of the Microsoft Project for designing Gantt Diagrams and keeping track of the project changes}{}
\cventry{2005--2006}{Contracted Researcher}{Vigo University, Spain}{Development of JPoEML, 
	a Java tool (mimic oriented) for designing and producing an E-Learning web environment that uses XML and J2EE to serve
	the desired learning models to the users over the web. This tool, created from scratch and based on the popular JFreeChart 
	Java Library, presented an editing environment similar to a UML Designing Tool used for creating and editing Learning Environments}{}{}
\cventry{1999--2005}{Network Administrator and Web Developer}{Freelance web developer and network administrator for local 
	and national enterprises. Design and deployment of a set of VPNs to provide media content to final clients through a Web
	Environment}{Vigo, Spain}{}{}

\section{Education}
\cventry{2000--2007}{Master's Degree in Telecommunications Engineering}{Vigo University}{}{}{}  % arguments 3 to 6 are optional
\cventry{2005--2007}{Master's Final Project}{Vigo University}{ASP Web Environment development}{}{}{}

\section{Papers and Conferences}
\cventry{Jun 2013}{SimCloud Paper and Presentation}{ESA Workshop}{ESOC, Darmstadt, Germany}{SimCloud: an Operational Simulator Development and Validation Cloud}{}
\cventry{Mar 2015}{Web Development Conference}{UPM TryIT}{UPM, Madrid, Spain}{User Focused Web Development}{}

\pagebreak

\section{Professional Training}
\cventry{Jun 2014}{Interviewing Software Engineers}{Amazon.com}{Amazon Spain, Madrid}{Theoretical and practical approach to hire the best software engineers by identifying their weakness and strengths}{}
\cventry{May 2013}{AWS Technical Professional}{The Server Labs}{Amazon.com}{AWS training targetting IT professionals designing Cloud architectures based on customer business requirements.}{}
\cventry{Apr 2010}{Agile Development Technologies}{The Server Labs}{ESOC, Darmstadt, Germany}{Software Development using Agile Metodology and SCRUM Techniques}{}
\cventry{Feb 2009}{Eclipse EMF, GEF and GMF Technologies}{OBEO Eclipse Foundation Member}{ESOC, Darmstadt, Germany}{Development of Eclipse Applications based on EMF/GEF and GMF}{}{}

\section{Languages}
\cvlanguage{Spanish}{Mother Tongue}{}
\cvlanguage{English}{Fluent}{More than eight years as primary professional language.}
\cvlanguage{German}{Good}{More than three years living in Germany, Goethe Institut level B2.}
\cvlanguage{Italian}{Basic}{Internal courses at ESOC/ESA.}

\section{Software Development}
%\cvskill{Linear}{Assembler, C, Pascal, Cobol, Fortran, Lisp.}
%\cvskill{Object Oriented}{Java, C++, Delphi, Visual Basic.}
\cvskill{Languages}{Java, C/C++, Pascal, Fortran, Delphi, Visual Basic.}
\cvskill{Eclipse}{PDE, RCP, SWT, EMF, GEF, GMF, OCL.}
\cvskill{J2EE}{JSF, JPA, Hibernate, JAX-RS, JAX-WS, Liquibase, Spring, Jersey.}
%\cvskill{Distributed}{RCP, Java RMI, CORBA.}
\cvskill{Scripting}{Python, Bash, Tcl, Perl.}
\cvskill{Web}{PHP, ASP, JSP, GWT, DHTML, XML, CSS, JS, Grunt, Handlebars}
\cvskill{CI}{Hudson/Jenkins, Maven, Jira, SVN, Redmine, Trac, Ant.}
%\cvskill{Agile}{Agilefant, IceScrum, XPlanner}
\cvskill{Others}{SQL, TestLink, \TeX.}

\section{Computer Environments}
\cvline{Unix}{Debian/SUSE/RedHat Linux, Solaris and Irix System Administration. LAMP.}
\cvline{Networking}{HTTP, DNS, SMTP, FTP, LDAP, Samba, DHCP, SSH, NFS, Security.}
\cvline{Virtualization}{Xen/XCP/XenServer, OpenVZ, VirtualBox, ESXi, Docker.}
\cvline{Public Cloud}{Amazon Web Services, CloudSigma, Google Compute Engine, CloudBees, Heroku.}
\cvline{Private Cloud}{OpenStack, OpenNebula, Eucalyptus.}
\cvline{Provisioning}{Chef, Puppet, Fabric.}
\cvline{J2EE Platforms}{Apache Tomcat, IBM Websphere, JBoss AS.}
\cvline{Space}{CCSDS TM/TC/SLE/CFDP, ECSS SW Standards}

\section{Documentation and References}
\cvline{}{\slshape{Available upon Request.}}
\end{document}


%% end of file `template_en.tex'.
