%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[blue]{casualg}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[blue]{casualg}                % idem
%\moderncvtheme[roman]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
\usepackage{hyperref}
\usepackage{fmtcount}

% adjust the page margins
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Alicia}
\familyname{Minguez}
\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{2530 29th Ave W}{Seattle WA 98199 | Green Card Holder}    % optional, remove the line if not wanted
\mobile{206 883 7299}
% \fax{fax (optional)}                          % optional, remove the line if not wanted
\email{alicia.minguez@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{Born in Madrid, 08 Sep 1982} % optional, remove the line if not wanted
%\photo[64pt]{picture.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
% \quote{Green Card Holder}                 % optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
\newenvironment{pitems}{
	\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
}{\end{itemize}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2004--2007}{Master's Degree in Electrical Engineering and \mbox{Information Technology}}{\mbox{Technische} Universitaet Darmstadt}
	{Darmstadt, Germany}{Double degree Spain/ Germany}{}
\cventry{2001--2007}{Master's Degree in Telecommunications Engineering}{Universidad Politecnica de Madrid}{Madrid, Spain}{}{}

\section{Work Experience}
\ccventry{2011--2017}{Senior Validation Engineer and Team Leader for Air Traffic Management}{Indra}{Madrid, Spain}
	{. Activities:
\begin{pitems}
\item $\bullet$ \textsl{Quality Assurance Lead:} Creation and execution of test cases and test scripts for functional and non-functional requirements at subsystem level. 
    These requirements are tested against the real Traffic Control infrastructure in order to assure the viability and stability of the software elements. 
    Creation and assessment of defects and recommendations for the enhancement of the software elements that help improve the quality of the final systems. 
    Analysis and ownership of test metrics and test results reports. 
\item $\bullet$ \textsl{Validation Engineering Team Manager:} Management and mentoring of a team of 5-10 people working on verification and validation of all 
    functional requirements at subsystem level for NATS project.
\item $\bullet$ \textsl{Systems Quality Control Engineer:} Design and execution of system and acceptance testing for the 
    Air Traffic Control Software ensuring the completion of the goals required by the client.
\item $\bullet$ \textsl{Technical Documentation:} Preparation and review of technical documentation in all phases of the Software Testing Life Cycle 
    following strict documentation models and standards used in the Air Traffic Control industry.
\end{pitems}}

\ccventry{2009--2011}{Ground Station Systems Engineer at European Space Agency}{Serco contractor on site at ESOC/ESA OPS-GSY section}{Darmstadt, Germany}
	{. Activities:
\begin{pitems}
\item $\bullet$ \textsl{Program Management:} Designed and Implemented new processes to improve system validation for ground segment software and hardware.
    Negotiated terms across organizations and stakeholders to deliver new mechanisms to unblock the business and align expectations.
\item $\bullet$ \textsl{Partner Contract Manager:} Coordinated the relationships with external partner teams that allowed the organization to 
    scale and deliver more software and hardware systems for ground station facilities.
\item $\bullet$ \textsl{Validation Engineer:} Creation and execution of end to end testing for Ground Segment. 
    Collaboration in the implementation of Radio Frequency Compatibility Tests for the Groud Segment / Spacecraft Equipment. 
\end{pitems}}
\ccventry{}{}{}{}{
\begin{pitems}
\item $\bullet$ \textsl{System Engineer:} Maintenance and operation of the ground segment reference \mbox{facilities} located in ESOC. 
		Management of hardware providers for the equipment used in the Ground Segment Reference Facilities.
\item $\bullet$ \textsl{Signal Engineer:} Engineer for Delta DOR (Differential One-way Ranging) used for interplanetary navigation.
		Collaboration in the implementation of radio frequency compatibility tests for the ground segment and spacecraft equipment.
\end{pitems}}
\cventry{2009--2009}{Antenna Software Engineer}{Inform GmbH contractor at MT Mechatronics GmbH}{Mainz, Germany}
{Construction and comissioning of a new antenna for the SAR-Lupe Gelsdorf project. 
		Design and development of local control panel for the antenna. 
		\mbox{Development} and validation of real time software for the Antenna Control Unit}{}{}

\cventry{2008--2008}{Research Engineer}{NEC Laboratories Europe}{Heidelberg, Germany}
	{Web services development of IP multimedia subsystem based IPTV applications for the project "IPTV Value Added Services"}{}{}

\cventry{2007--2008}{Young Graduate Trainee}{ESOC/ESA OPS-GDS section}{Darmstadt, Germany}
	{Definition and analysis of software requirements for Gaia spacecraft simulator. 
		Collaboration in a generic software requirements specification document for spacecraft simulators. 
		Definition of requirements and support for Lisa Pathfinder spacecraft simulator}{}{}

\cventry{2006--2007}{Diploma Thesis}{Honda Research Institute Europe GmbH}{Offenbach, Germany}
	{\mbox{Digital} image processing for the visual system of Honda's robot Asimo}{}{}

\cventry{2005--2006}{Student Position}{Deutsche Telekom AG}{Darmstadt, Germany}{Development and testing of central identity management system for IT-Security}{}{}

\section{Certifications}
\cventry{2015}{International Software Testing Qualification Board}{ISTQB Foundational certified}{}{}{}{}

\section{Languages}
\cvlanguage{Spanish}{Mother Tongue}{}
\cvlanguage{English}{Fluent}{Several years working in English in different companies.}
\cvlanguage{German}{Fluent}{Seven years living and working in Germany.}
\cvlanguage{French}{Basic}{}

\section{Professional Skills}
\cvskill{Programming}{C++, IEC 61131-3, Java, Matlab, VB, JavaScript}
\cvskill{Tools}{Jira, IBM Rational Change, DOORS, Eclipse, TwinCAT, MS-Office}
\cvskill{Technologies}{PLC Programming, MFC, Web Services, UML, XML, SQL}

\end{document}


%% end of file `template_en.tex'.
